Placeholder

### 2021-02-18 Paper_Histograms.Rmd
Removed unused packages from library chunk and added installations for used packages

#install.packages("multipanelfigure")

@@

```{r read in data }

# Read in data
library(knitr)
library(summarytools)
library(psych)
library(polycor)
library(corrplot)
library(patchwork)
library(broom)
library(tidyverse)
library(ggpubr)
library(cowplot)
library(gridExtra)

>>>>

#install.packages("knitr")
#install.packages("tidyverse")
#install.packages("ggpubr")
#install.packages("cowplot")
#install.packages("gridExtra")
#install.packages("grid")

@@

```{r read in data}

# Read in data
library(knitr)
library(tidyverse)
library(ggpubr)
library(cowplot)
library(gridExtra)
library(grid)
